%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{tex/resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage{hyperref}




%------------------------------------------------

\name{Michael Leong} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.
\address{408-710-0887 $\vert$ michaelleong1229@gmail.com $\vert$ \underline{\href{https://www.linkedin.com/in/m-leong/}{https://www.linkedin.com/in/m-leong/}} $\vert$ \underline{\href{https://github.com/leongmichael}{https://github.com/leongmichael}}} % Contact information

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
	\textbf{Leland High School} \hfill \textit{Class of 2024} \\ 
	Cumulative GPA: 4.00 (Unweighted)
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{FRC 604 Quixilver Robotics}{June 2020 - Present}{VP of Engineering}{San Jose, CA}
		\item Lead team in all branches of technical robot design. Responsible for training new members and contributing to robot development.
        \item Developed time-optimal trajectory optimization software utilizing non-linear optimization algorithms using our robot’s kinodynamic constraints.
        \item Developed particle filter robot localization software using both odometry from motor encoders and computer vision utilizing PhotonVision/OpenCV to detect AprilTag targets.
        \item Designed numerous robot mechanisms including linear slides and a four-bar linkage arm.
        
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Lawrence Berkeley National Laboratory}{July 2023 - Present}{Research Intern}{Berkeley, CA}
		\item Developed a web-based tool for assessing the building energy demand flexibility of small and medium-sized businesses.
		\item Set-up MongoDB, Express, React, Node (MERN) web stack and GitHub Actions automated tests.
        \item Ported existing building data to MongoDB and implemented REST API to communicate between server and client.
        \item Implemented and optimized existing demand flexibility algorithms to the application.
        
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Invantest}{June 2022 - July 2022}{Intern}{San Jose, CA}
		\item Optimized existing Linux shell scripts for setting up software for new recruits.
		\item Tested the accuracy of AI detection models for defective semiconductor wafers.
	\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

	\begin{rSubsection}{VelocityDraft}{}{GitHub Link: \underline{\href{https://github.com/shuklabhay/VelocityDraft}{https://github.com/shuklabhay/VelocityDraft}}}{}
		\item Created college essay writing scheduler based on writing speed, deadline, and number of necessary revisions. Created with Firebase, Express, React, Node (FERN) web stack.
		\item Received 3rd place submission while competing against 120+ people.
	\end{rSubsection}

    \begin{rSubsection}{FRC 604 2022 Robot Code}{}{GitHub Link: \underline{\href{https://github.com/frc604/2022-public}{https://github.com/frc604/2022-public}}}{}
		\item Includes robot code, swerve drive trajectory optimization, and particle filter localization
        \item Enabled team to receive Autonomous Award and Innovation in Controls Award in the 2022 season
	\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
    %	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Programming Languages & Java, JavaScript, Python, TypeScript \\
		Libraries + Frameworks & Flask, Firebase, MongoDB, Express, React, Node, React-Native, Expo, Matplotlib, Numpy \\
		Tools & Git, Onshape, Fusion360, Photoshop, Vegas Pro
	\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
    % HONORS & AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Awards}

    \begin{itemize}
        \setlength\itemsep{-0.7em} % Adjust the space between items
        \item FIRST Dean's List Semi-Finalist \hfill 2023
        \item OneHacks III 3rd place submission \hfill 2023
        \item Creativity Award sponsored by Rockwell Automation (Championship Level) \hfill 2023
        \item FIRST Championship Carver Division Winner \hfill 2022
        \item Innovation in Controls Award (2x) \hfill 2022, 2023
        \item Autonomous Award Sponsored by Ford (2x) \hfill 2021, 2022

    \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

	%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
